Figures

### 2019-08-06 figures/07_model-selection.Rmd
align panel titles

gg_tp_fe <- 
  ggplot(data = gg_tp) + 
  geom_pointrange(aes(x = pretty, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) + 
  expand_limits(y = -1.8) +
  geom_rect(ymin = -0.6, ymax = -0.6 - 2, xmin = 0, xmax = nrow(gg_tp) + 1, 
              fill = "transparent") +
  geom_text(aes(x = pretty, label = pretty, color = signif), 
            y = -0.65, vjust = 0.5, hjust = "right") + 
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  scale_y_continuous(breaks = seq(from = -0.6, to  = 0.4, by = 0.2), 
                     labels = scales::number_format(accuracy = 0.1)) +
  coord_flip() +
  theme(axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.title.y = element_blank()) + 
    facet_wrap(~category, strip.position = "left", ncol = 1, scales = "free_y",
               as.table = FALSE) +
    theme(panel.spacing = unit(0, "lines"), 
          strip.placement = "outside", 
          strip.background = element_blank(), 
          axis.title.y = element_blank()) + 
        ylab("Standardized slope") + theme(legend.position = 0) + 
        ggtitle("TP") + xlab("") +
  theme(panel.background = element_rect(fill = "transparent", color = NA),
        plot.background = element_rect(fill = "transparent", color = NA), 
        panel.grid = element_blank(),
        rect = element_rect(fill = "transparent")) + 
    annotate(x=0, xend=0, y=-0.6, yend=0.4, 
             colour="black", lwd=0.9, geom="segment") 
```

@@

gg_tp_re <- ggplot(data = fit_tp$re) +
  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = as.numeric(fit_tp$re_global["50%"])) +
  coord_flip() +
  cowplot::theme_cowplot() +
  theme(rect = element_rect(fill = "transparent")) +
  ggtitle("TP ~ Ag slope") + xlab("Zone ID") + ylab("") +
  theme(legend.position = 0)

@@

gg_tn_fe <- 
  ggplot(data = gg_tn) + 
  geom_pointrange(aes(x = pretty, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) + 
  expand_limits(y = c(-0.6, 1.6)) +
  geom_rect(ymin = 0.44, ymax = 0.44 + 2, xmin = 0, xmax = nrow(gg_tn) + 1, 
              fill = "transparent") +
  geom_text(aes(x = pretty, label = pretty, color = signif), 
            y = 0.44, vjust = 0.5, hjust = "left") + 
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
    geom_hline(yintercept = 0) +
  scale_y_continuous(breaks = seq(from = -0.6, to  = 0.4, by = 0.2), 
                     labels = scales::number_format(accuracy = 0.1)) +
  coord_flip() +
  theme(axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.title.y = element_blank()) + 
    facet_wrap(~category, strip.position = "right", ncol = 1, scales = "free_y",
               as.table = FALSE) +
    theme(panel.spacing = unit(0, "lines"), 
          strip.placement = "outside", 
          strip.background = element_blank(), 
          axis.title.y = element_blank()) + 
        ylab("Standardized slope") + theme(legend.position = 0) + 
        ggtitle("TN") + xlab("") +
  theme(panel.background = element_rect(fill = "transparent"), 
        panel.grid = element_blank(),
        rect = element_rect(fill = "transparent")) + 
    annotate(x=0, xend=0, y=-0.6, yend=0.4, 
             colour="black", lwd=0.9, geom="segment")

@@

gg_tn_re <- ggplot(data = fit_tn$re) +
  geom_hline(yintercept = as.numeric(fit_tn$re_global["50%"])) +
  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  coord_flip() +
  cowplot::theme_cowplot() +
  theme(rect = element_rect(fill = "transparent")) +
  ggtitle("TN ~ corn slope") + xlab("Zone ID") + ylab("") +
  theme(legend.position = 0)

@@

group_by(re_global, response) %>%
  arrange(desc(`50%`))

gg_tn <- ggplot(data = dplyr::filter(re_global, response == "tn")) +
    geom_pointrange(aes(x = term, y = `50%`, 
                      ymin = `5%`, ymax = `95%`), color = "red") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  expand_limits(y = -0.2) +
  coord_flip() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        strip.placement = "outside", 
        strip.background = element_blank(), 
        panel.background = element_rect(fill = "transparent", color = NA),
        plot.background = element_rect(fill = "transparent", color = NA), 
        panel.grid = element_blank(),
        rect = element_rect(fill = "transparent"), 
        axis.line = element_line(), 
        axis.text.y = element_blank()) +
  ggtitle("TN")

gg_tp <- ggplot(data = dplyr::filter(re_global, response == "tp")) +
    geom_pointrange(aes(x = term, y = `50%`, 
                      ymin = `5%`, ymax = `95%`), color = "red") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  expand_limits(y = -0.2) +
  coord_flip() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        strip.placement = "outside", 
        strip.background = element_blank(), 
        panel.background = element_rect(fill = "transparent", color = NA),
        plot.background = element_rect(fill = "transparent", color = NA), 
        panel.grid = element_blank(),
        rect = element_rect(fill = "transparent"), 
        axis.line = element_line()) +
  ggtitle("TP")

cowplot::plot_grid(gg_tp, gg_tn, rel_widths = c(1, 0.8))
```

>>>>

gg_tp_fe <- 
  ggplot(data = gg_tp) + 
  geom_pointrange(aes(x = pretty, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) + 
  expand_limits(y = -1.8) +
  geom_rect(ymin = -0.6, ymax = -0.6 - 2, xmin = 0, xmax = nrow(gg_tp) + 1, 
              fill = "transparent") +
  geom_text(aes(x = pretty, label = pretty, color = signif), 
            y = -0.65, vjust = 0.5, hjust = "right") + 
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  scale_y_continuous(breaks = seq(from = -0.6, to  = 0.4, by = 0.2), 
                     labels = scales::number_format(accuracy = 0.1)) +
  coord_flip() +
  theme(axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.title.y = element_blank()) + 
    facet_wrap(~category, strip.position = "left", ncol = 1, scales = "free_y",
               as.table = FALSE) +
    theme(panel.spacing = unit(0, "lines"), 
          strip.placement = "outside", 
          strip.background = element_blank(), 
          axis.title.y = element_blank()) + 
        ylab("Standardized slope") + theme(legend.position = 0) + 
        ggtitle("TP") + xlab("") +
  theme(panel.background = element_rect(fill = "transparent", color = NA),
        plot.background = element_rect(fill = "transparent", color = NA), 
        panel.grid = element_blank(),
        rect = element_rect(fill = "transparent"), 
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
    annotate(x=0, xend=0, y=-0.6, yend=0.4, 
             colour="black", lwd=0.9, geom="segment") 
```

@@

gg_tp_re <- ggplot(data = fit_tp$re) +
  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = as.numeric(fit_tp$re_global["50%"])) +
  coord_flip() +
  cowplot::theme_cowplot() +
  theme(rect = element_rect(fill = "transparent")) +
  ggtitle("TP ~ Ag slope") + xlab("Zone ID") + ylab("") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  theme(legend.position = 0)

@@

gg_tn_fe <- 
  ggplot(data = gg_tn) + 
  geom_pointrange(aes(x = pretty, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) + 
  expand_limits(y = c(-0.6, 1.6)) +
  geom_rect(ymin = 0.44, ymax = 0.44 + 2, xmin = 0, xmax = nrow(gg_tn) + 1, 
              fill = "transparent") +
  geom_text(aes(x = pretty, label = pretty, color = signif), 
            y = 0.44, vjust = 0.5, hjust = "left") + 
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
    geom_hline(yintercept = 0) +
  scale_y_continuous(breaks = seq(from = -0.6, to  = 0.4, by = 0.2), 
                     labels = scales::number_format(accuracy = 0.1)) +
  coord_flip() +
  theme(axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.title.y = element_blank()) + 
    facet_wrap(~category, strip.position = "right", ncol = 1, scales = "free_y",
               as.table = FALSE) +
    theme(panel.spacing = unit(0, "lines"), 
          strip.placement = "outside", 
          strip.background = element_blank(), 
          axis.title.y = element_blank()) + 
        ylab("Standardized slope") + theme(legend.position = 0) + 
        ggtitle("TN") + xlab("") +
  theme(panel.background = element_rect(fill = "transparent"), 
        panel.grid = element_blank(),
        rect = element_rect(fill = "transparent"), 
        plot.title = element_text(hjust = 0.5, face = "bold")) + 
    annotate(x=0, xend=0, y=-0.6, yend=0.4, 
             colour="black", lwd=0.9, geom="segment")

@@

gg_tn_re <- ggplot(data = fit_tn$re) +
  geom_hline(yintercept = as.numeric(fit_tn$re_global["50%"])) +
  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  coord_flip() +
  cowplot::theme_cowplot() +
  theme(rect = element_rect(fill = "transparent")) +
  ggtitle("TN ~ corn slope") + xlab("Zone ID") + ylab("") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  theme(legend.position = 0)

@@

# group_by(re_global, response) %>%
#   arrange(desc(`50%`))

gg_tn <- ggplot(data = dplyr::filter(re_global, response == "tn")) +
    geom_pointrange(aes(x = term, y = `50%`, 
                      ymin = `5%`, ymax = `95%`), color = "red") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  expand_limits(y = -0.2) +
  coord_flip() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        strip.placement = "outside", 
        strip.background = element_blank(), 
        panel.background = element_rect(fill = "transparent", color = NA),
        plot.background = element_rect(fill = "transparent", color = NA), 
        panel.grid = element_blank(),
        rect = element_rect(fill = "transparent"), 
        axis.line = element_line(), 
        axis.text.y = element_blank()) +
  ggtitle("TN") + 
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))

gg_tp <- ggplot(data = dplyr::filter(re_global, response == "tp")) +
    geom_pointrange(aes(x = term, y = `50%`, 
                      ymin = `5%`, ymax = `95%`), color = "red") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  expand_limits(y = -0.2) +
  coord_flip() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        strip.placement = "outside", 
        strip.background = element_blank(), 
        panel.background = element_rect(fill = "transparent", color = NA),
        plot.background = element_rect(fill = "transparent", color = NA), 
        panel.grid = element_blank(),
        rect = element_rect(fill = "transparent"), 
        axis.line = element_line()) +
  ggtitle("TP") + 
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))

cowplot::plot_grid(gg_tp, gg_tn, rel_widths = c(1, 0.75))
```
